Parity games in pushdown systems with parameters

### 2023-06-20 reachability/article.tex
up

% \author{Stefan G\"oller}{University of Kassel \and School of Electrical Engineering and Computer Science \and Kassel, Germany }{stefan.goeller@uni-kassel.de}{}{The author was supported by the Agence Nationale de la Recherche grant no.  ANR-17-CE40-0010.}
\author{Mathieu Hilaire}{Université Paris-Saclay\and
CNRS\and
ENS Paris-Saclay\and
Laboratoire Méthodes Formelles (LMF)\and
Gif-sur-Yvette, France
}{hilaire@lsv.fr}{}{This work was partly done while the author was supported by the 
Agence Nationale de la Recherche grant no.  ANR-17-CE40-0010.}

@@

\acknowledgements{The author would like to thank Benedikt Bollig and Stefan G\"oller for helpful discussions and feedback.}

>>>>

% \author{Stefan G\"oller}{University of Kassel \and School of Electrical Engineering and Computer Science \and Kassel, Germany }{stefan.goeller@uni-kassel.de}{}{The author was supported by the Agence Nationale de la Recherche grant no.  ANR-17-CE40-0010.}
\author{Mathieu Hilaire}{Université Paris-Saclay,
CNRS,
ENS Paris-Saclay,
LMF,
Gif-sur-Yvette, France
}{hilaire@lsv.fr}{}{This work was partly done while the author was supported by the 
Agence Nationale de la Recherche grant no.  ANR-17-CE40-0010.}

@@

\acknowledgements{The author would like to thank Benedikt Bollig, Stefan G\"oller and Alain Finkel for helpful discussions and feedback.}
